Flabby and injective objects in toposes

### 2025-12-17 paper-flabby-objects.tex
typo
to do

>>>>

Cite:
https://arxiv.org/abs/1802.00960

https://ncatlab.org/nlab/show/algebraically+injective+object

https://www.cse.chalmers.se/~coquand/course231.pdf#page=23
Perhaps flabby objects could be called "contractible objects"?

cite
https://arxiv.org/pdf/1903.01211
Thm. 19, 20
for discussion of "functionally flabby ↔ injective"

Cite general idea or injectivity aspects of:
https://1lab.dev/Data.Partial.Properties.html
